Title here

### 2020-06-24 submission_ams/submission_ams.tex
refactoring

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{setspace}
\setstretch{2}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin = 1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{caption}
\usepackage{blindtext}
\usepackage[left]{lineno}
\linenumbers

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\newpage

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Phylogenies are a key part of research in all areas of biology. Tools that automatize
  some parts of the process of phylogenetic reconstruction (mainly character matrix construction)
  have been developed for the advantage of both specialists in the field of phylogenetics and nonspecialists.
  However, interpretation of results, comparison with previously available phylogenetic
  hypotheses, and choosing of one phylogeny for downstream analyses and discussion still impose difficulties
  to one that is not a specialist either on phylogenetic methods or on a particular group of study.
\item
  Physcraper is an open‐source, command-line Python program that automatizes the update of published
  phylogenies by making use of public DNA sequence data and taxonomic information,
  providing a framework for comparison of published phylogenies with their updated versions.
\item
  Physcraper can be used by the nonspecialist, as a tool to generate phylogenetic
  hypothesis based on already available expert phylogenetic knowledge.
  Phylogeneticists and group specialists will find it useful as a tool to facilitate comparison
  of alternative phylogenetic hypotheses (topologies).
  \textbf{\emph{Is physcraper intended for the nonspecialist?? We have two types of nonspecialists:
  the ones that do not know about phylogenetic methods and the ones that might know
  about phylogenetic methods but do not know much about a certain biological group.}}
\item
  Physcraper implements node by node/topology comparison of the the original and the updated
  trees using the conflict API of OToL, and summarizes differences.
\item
  We hope the physcraper workflow demonstrates the benefits of opening results in phylogenetics and encourages researchers to strive for better data sharing practices.
\item
  Physcraper can be used with any OS. Detailed instructions for installation and
  use are available at \url{https://github.com/McTavishLab/physcraper}.
\end{enumerate}

\newpage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Obtention of molecular or morphological character data -- get DNA from some organisms
  and sequence it, or get it from an online nucleotide data repository, such as GenBank (Benson et al. \protect\hyperlink{ref-benson2000genbank}{2000}; Wheeler et al. \protect\hyperlink{ref-wheeler2000database}{2000}).
\item
  Assemble a hypothesis of homology -- Create a matrix of your character data, by
  aligning the sequences, in the case of molecular data. Make sure thay are paralogs!
\item
  Analyse this hypothesis of homology to infer phylogenetic relationships among
  the organisms you are studying -- Use different available programs to infer molecular
  evolution, trees and times of divergence.
\item
  Discuss the inferred relationships in the context of previous hypothesis, the
  biology and biogeography of the organisms, etc. -- Answer the question, \emph{is this phylogenetic solution fair/reasonable?}
\end{enumerate}

@@

In the past decade, various studies have developed solutions to automatize the first and second steps, by creating
pipelines that mine already available molecular data from the GenBank repository (Benson et al. \protect\hyperlink{ref-benson2000genbank}{2000}; Wheeler et al. \protect\hyperlink{ref-wheeler2000database}{2000}),
to obtain homologous characters that can be used for phylogenetic reconstruction.
These tools have been presented as aid for the nonspecialist to decrease some of
the difficulties in the generation of phylogenetic knowledge. However, they are
not that often used as so, suggesting that there are still difficulties for the nonspecialist.
The phylogenetic community has some reserves towards these tools, too. Mainly because they sometimes act as a black box.
However, automatizing the assembly of the character data set is a crucial step towards
reproducibility for a task that was otherwise primarily artisanal and hence largely
non-reproducible.

@@

Public phylogenies can be updated with the ever increasing amount of genetic data that is available on GenBank (Benson et al. \protect\hyperlink{ref-benson2000genbank}{2000}; Wheeler et al. \protect\hyperlink{ref-wheeler2000database}{2000}).

@@

The goal of Physcraper is to build upon previous phylogenetic knowledge,
allowing a direct comparison between existing phylogenies and phylogenies that are constructed
using new genetic data retrieved from a public nucleotide database (i.e., GenBank (Benson et al. \protect\hyperlink{ref-benson2000genbank}{2000}; Wheeler et al. \protect\hyperlink{ref-wheeler2000database}{2000})).

@@

\begin{itemize}
\tightlist
\item
  The study tree is a published phylogenetic tree stored in the OToL database, phylesystem (McTavish et al. \protect\hyperlink{ref-mctavish2015phylesystem}{2015}). The main
  reason for this is that trees in phylesystem have a set of user defined characteristics
  that are essential for automatizing the phylogeny update process. The most relevant of these being the definition of ingroup and outgroup. Outgroup and ingroup taxa in the original tree are identified and tagged. This allows to automatically set the root for the updated tree on the next steps of the pipeline.
  A user can choose from the `r rotl::tol\_about()\$num\_source\_trees' published trees supporting the resolved node of the synthetic tree in the OToL website (\textless{}\textgreater{}). If the tree you are interested in updating is not in there, you can upload it via OToL's curator tool (\textless{}\url{https://tree.opentreeoflife.org/curator}).
\item
  The alignment should be a gene alignment that was used to generate the tree. The original
  alignments are usually stored in a public repository such as TreeBase (Piel et al. \protect\hyperlink{ref-piel2009treebase}{2009}; Vos et al. \protect\hyperlink{ref-vos2012nexml}{2012}),
  DRYAD (\url{http://datadryad.org/}), or the journal were the tree was originally published.
  If the alignment is stored in TreeBase, \texttt{physcraper} can download it directly,
  either from the TreeBASE website (\url{https://treebase.org/})
  or through the TreeBASE GitHub repository (SuperTreeBASE; \url{https://github.com/TreeBASE/supertreebase}).
  If the alignment is on another repository, or provided personally by the owner, a copy of it has to be
  downloaded by the user, and it's local path has to be provided as an argument.
\item
  A taxon name matching step is performed to verify that all taxon names on the tips
  of the tree are in the DNA character matrix and vice versa.
\item
  A ``.csv'' file with the summary of taxon name matching is produced for the user.
\item
  Unmatched taxon names are dropped from both the tree and alignment.
  Technically, just one matching name is needed to perform the searches. Please, see next section.
\item
  A ``.tre'' file and a ``.fas'' file containing only the matched taxa are generated and saved in the \texttt{inputs} folder to be used in the following steps.
\end{itemize}

@@

  Users can provide a search taxon that is either a more or a less inclusive
  clade relative to the ingroup of the original phylogeny. If the search taxon is more inclusive, the sequence search will be performed outside the MRCAT of the matched taxa, e.g., including all taxa within
  the family or the order that the ingroup belongs to. If the search taxon is a less inclusive clade, the users can focus on enriching a particular clade/region within the ingroup of the phylogeny.
\item
  The Basic Local Alignment Search Tool, BLAST {[}Altschul et al. (\protect\hyperlink{ref-altschul1990basic}{1990}); altschul1997gapped{]} is used to identify
  similarity between DNA sequences within the search taxon in a nucleotide
  database, and the remaining sequences on the alignment.
  The BLAST command line tools (Camacho et al. \protect\hyperlink{ref-camacho2009blast}{2009}) are used for both web-based and local-database searches.
\item
  A pairwise alignment-against-all BLAST search is performed. This means that each sequence
  in the alignment is BLASTed against DNA sequences in a nucleotide database constrained to the search
  taxon. Results from each one of these BLAST runs are recorded, and matched sequences are saved
  along with their corresponding identification numbers (accesion numbers in the case of the GenBank database). This information will be used later to store the whole sequences in a dedicated library within the physcraper folder, allowing for secondary analyses to run significantly faster.
\item
  The DNA sequence similarity search can be done on a local database that is easily
  setup by the user. In this case, the BLASTn algorithm is used to performs the similarity search.
\item
  The search can also be performed remotely, on the NCBI database. In this case, the
  bioPython BLAST algorithm is used to perform the similarity search.
\item
  Matched sequences below an e-value, percentage similarity, and outside a minimum
  and maximum length threshold are discarded. This filtering leaves out genomic sequences.
  All acepted sequences are asigned an internal identifier, and are further filtered.
\item
  Because the original alignments usually lack database id numbers, a filtering
  step is needed. Accepted sequences that belong to the
  same taxon of the query sequence, and that are either identical or shorter than
  the original sequence are discarded. Only longer sequences belonging to the
  same taxon as the orignal sequence will be considered further for analysis.
\item
  Among the remaining filtered sequences, there are usually several exemplars per taxon.
  Although it can be useful to keep some of them to, for example, investigate monophyly
  within species, there can be hundreds of exemplar sequences per taxon for some markers.
  To control the number of sequences per taxon in downstream analyses,
  5 sequences per taxon are chosen at random. This number is set by default but can be modified by the user.
\item
  Reverse complement sequences are identified and translated.
\item
  Users can choose to perform a more ``cycles'' of sequence similarity search, by blasting the newly found sequences. This can be done iteratively, but by default only sequences in the alignment are blasted. \textbf{\emph{Is there an argument to control the number of cycles of blast searches with new sequences?}}
\item
  Accepted sequences are downloaded in full, and stored as a local database in a directory that is globally accesible (physcraper/taxonomy), so they are accesible for further runs.
\item
  A fasta file containing all filtered and processed sequences resulting from the BLAST search is generated for the user.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The software MUSCLE (Edgar \protect\hyperlink{ref-edgar2004muscle}{2004}) is implemented to perform alignments.
\item
  First, all new sequences are aligned using default MUSCLE options.
\item
  Then, a MUSCLE profile alignment is performed, in which the original alignment
  is used as a template to align new sequences. This ensures that the final alignment
  follows the homology criteria established by the original alignment.
\item
  The final alignment is not further processed automatically. We encourage users
  to check it either by eye and perform manual refinement or using any of the many
  tools for alignment processing, to eliminate columns with no information.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  A gene tree is reconstructed for each alignment provided, using the software RAxML (Stamatakis \protect\hyperlink{ref-stamatakis2014raxml}{2014})
  with 100 classic bootstrap (Felsenstein \protect\hyperlink{ref-felsenstein1985confidence}{1985}) replicates by default. The number of bootsrap replicates can be modified by the user.
  Other type of bootstrap that I think is not yet incorporated into physcraper is the Transfer Bootstrap Expectation (TBE) recently proposed in Lemoine et al. (\protect\hyperlink{ref-lemoine2018renewing}{2018}).
\item
  The final result is an updated phylogenetic hypothesis for each of the genes provided in the alignment.
\item
  Tips on all trees generated by physcraper are defined by a taxon name space, allowing to perform comparisons and conflict analyses.
\item
  Robinson Foulds metrics
\item
  Describe what a conflict analysis is: Node by node comparison of the resulting clades compared to
\item
  For the conflict analysis to be meaningful, the root of the tree ineeds to be accurately defined.
\item
  Currently, the root is determined by finding the parent node of the sequences that do not belong to the ingroup/ search taxon. This ensures a correct rooting of the tree even when the search taxon is more inclusive than the ingroup.
\item
  Conflict information can only be generated in the context of the whole Open Tree of
  Life. Otherwise, it is not really possible to get conflict data.
  \textbf{\emph{- One way to compare two independent phylogenetic trees is to compare them both to
  the synthetic OToL and then measure how well they do against each other}}
\end{itemize}

@@

The genus \emph{Ilex} is the only extant clade within the family Aquifoliaceae, order Aquifoliales of flowering plants.
It encompasses between 400-600 living species. A review of litterature shows that there are three published phylogenetic trees, showing relationships within the hollies.
The first one has been made available both on OToL phylesystem and synth tree, and on treeBASE, it samples 48 species.
The second has not been made available anywhere, not even in supplementary data of the journal.
\textbf{\emph{Contact authors? They seem old school, probably do not wanna share their data.}}
The most recent one has been made available in the OToL Phylesystem and DRYAD. It is the best sampled yet, with 200 species. However,
it has not been added to the syntehtic tree yet.
This makes it a perfect case to test the basic functionalities of physcraper: we know that the sequences of the most recently published tree have been made available on the GenBank database (Benson et al. \protect\hyperlink{ref-benson2000genbank}{2000}; Wheeler et al. \protect\hyperlink{ref-wheeler2000database}{2000}). Updating the oldest tree, we should get something very similar to the newest tree.

@@

Let's be more specific now about our X group and say it is the Ascomycota.
The best tree currently available in OToL was published by Schoch et al. (\protect\hyperlink{ref-schoch2009ascomycota}{2009}).
The first step, is to get the Open Tree of Life study id. There are some options to do this:
- You can go to the Open Tree of Life website and browse until you find it, or
- you can get the study id using R tools:
- By using the TreeBase ID of the study (which is not fully exposed on the
TreeBase website home page of the study, so you have to really look it up manually):

@@

Phylogeny of the Testudines 6 tips from Crawford et al. (\protect\hyperlink{ref-crawford2012more}{2012})
There is just one tree in OToL.
There is just one alignment on \href{https://treebase.org/treebase-web/search/study/matrices.html?id=12742}{treebase} with all the 1 145 loci.

@@

Describe again statistics to compare phylogenies provided by physcraper via OpenTreeOfLife.
Mention statistics provided by other tools: PhyloExplorer (Ranwez et al. \protect\hyperlink{ref-ranwez2009phyloexplorer}{2009}).
Compare and discuss.

@@

How can it be used for the advantage of the field:
- rapid phylogenetic placing of newly discovered species, as mentioned in Webb et al. (\protect\hyperlink{ref-webb2010biodiversity}{2010})
- obtain trees for ecophylogenetic studies, as mentioned in Helmus and Ives (\protect\hyperlink{ref-helmus2012phylogenetic}{2012})
- one day could be used to sistematize nucleotide databases, such as Genbank (Benson et al. \protect\hyperlink{ref-benson2000genbank}{2000}; Wheeler et al. \protect\hyperlink{ref-wheeler2000database}{2000}), as mentioned in San Mauro and Agorreta (\protect\hyperlink{ref-san2010molecular}{2010}), i.e., curate ncbi taxonomic assignations.
- allows to generate custom species trees for downstream analyses, as mentioned in Stoltzfus et al. (\protect\hyperlink{ref-stoltzfus2013phylotastic}{2013})

Things that physcraper does not do:
- analyse the whole GenBank database (Benson et al. \protect\hyperlink{ref-benson2000genbank}{2000}; Wheeler et al. \protect\hyperlink{ref-wheeler2000database}{2000}) to find homolog regions suitable to reconstruct phylogenies, as mentioned in Antonelli et al. (\protect\hyperlink{ref-antonelli2017toward}{2017}). There are already some very good tools that do that.
- provide basic statistics on data availability to assemble molecular datasets, as mentioned by Ranwez et al. (\protect\hyperlink{ref-ranwez2009phyloexplorer}{2009}). Phyloexplorer does this?
- it is not a tree repo, as phylota is, mentioned in Deepak et al. (\protect\hyperlink{ref-deepak2014evominer}{2014})

@@

Sanderson et al. (\protect\hyperlink{ref-sanderson2008phylota}{2008})\strut

@@

finds sets of DNA homologs on the GenBank database; phylogenetic reconstruction\strut

@@

Wu and Eisen (\protect\hyperlink{ref-wu2008simple}{2008})\strut

@@

baited search; protein markers on phylogenomic data; personal database of genomes or metagenomic data, manually downloaded either from a public database or from private data; phylogenetic reconstruction\strut

@@

Smith et al. (\protect\hyperlink{ref-smith2009mega}{2009})\strut

@@

Baited search of DNA markers on the GenBank database; phylogenetic reconstruction\strut

>>>>

\documentclass[draft]{ametsoc}
\usepackage{color}
\usepackage{hyperref}
\journal{jhm}
%  Please choose a journal abbreviation to use above from the following list:
%
%   jamc     (Journal of Applied Meteorology and Climatology)
%   jtech     (Journal of Atmospheric and Oceanic Technology)
%   jhm      (Journal of Hydrometeorology)
%   jpo     (Journal of Physical Oceanography)
%   jas      (Journal of Atmospheric Sciences)
%   jcli      (Journal of Climate)
%   mwr      (Monthly Weather Review)
%   wcas      (Weather, Climate, and Society)
%   waf       (Weather and Forecasting)
%   bams (Bulletin of the American Meteorological Society)
%   ei    (Earth Interactions)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Citations should be of the form ``author year''  not ``author, year''
\bibpunct{(}{)}{;}{a}{}{,}
\title{Title here}

\authors{Andrew N. Other
and Fred T. Secondauthor
\thanks{Current address: Some other place, Germany}}
\affiliation{American Meteorological Society,Boston, Massachusetts}

\extraauthor{Ping Lu
\correspondingauthor{Ping Lu,American Meteorological Society, 45 Beacon St., Boston, MA 02108.}
}
\extraaffil{Princeton University}
\email{groupleader@unknown.uu}
\extraauthor{Miao Yu
\thanks{Current address: Some other place, Canada}
}
\extraaffil{University of Waterloo}

% pandoc header
\abstract{some abstract}
\begin{document}
\maketitle
\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Obtention of molecular or morphological character data -- get DNA from
  some organisms and sequence it, or get it from an online nucleotide
  data repository, such as GenBank (Benson et al. 2000; Wheeler et al.
  2000).
\item
  Assemble a hypothesis of homology -- Create a matrix of your character
  data, by aligning the sequences, in the case of molecular data. Make
  sure thay are paralogs!
\item
  Analyse this hypothesis of homology to infer phylogenetic
  relationships among the organisms you are studying -- Use different
  available programs to infer molecular evolution, trees and times of
  divergence.
\item
  Discuss the inferred relationships in the context of previous
  hypothesis, the biology and biogeography of the organisms, etc. --
  Answer the question, \emph{is this phylogenetic solution
  fair/reasonable?}
\end{enumerate}

@@

In the past decade, various studies have developed solutions to
automatize the first and second steps, by creating pipelines that mine
already available molecular data from the GenBank repository (Benson et
al. 2000; Wheeler et al. 2000), to obtain homologous characters that can
be used for phylogenetic reconstruction. These tools have been presented
as aid for the nonspecialist to decrease some of the difficulties in the
generation of phylogenetic knowledge. However, they are not that often
used as so, suggesting that there are still difficulties for the
nonspecialist. The phylogenetic community has some reserves towards
these tools, too. Mainly because they sometimes act as a black box.
However, automatizing the assembly of the character data set is a
crucial step towards reproducibility for a task that was otherwise
primarily artisanal and hence largely non-reproducible.

@@

Public phylogenies can be updated with the ever increasing amount of
genetic data that is available on GenBank (Benson et al. 2000; Wheeler
et al. 2000).

@@

The goal of Physcraper is to build upon previous phylogenetic knowledge,
allowing a direct comparison between existing phylogenies and
phylogenies that are constructed using new genetic data retrieved from a
public nucleotide database (i.e., GenBank (Benson et al. 2000; Wheeler
et al. 2000)).

@@

\begin{itemize}
\tightlist
\item
  The study tree is a published phylogenetic tree stored in the OToL
  database, phylesystem (McTavish et al. 2015). The main reason for this
  is that trees in phylesystem have a set of user defined
  characteristics that are essential for automatizing the phylogeny
  update process. The most relevant of these being the definition of
  ingroup and outgroup. Outgroup and ingroup taxa in the original tree
  are identified and tagged. This allows to automatically set the root
  for the updated tree on the next steps of the pipeline. A user can
  choose from the `r rotl::tol\_about()\$num\_source\_trees' published
  trees supporting the resolved node of the synthetic tree in the OToL
  website (\textless{}\textgreater{}). If the tree you are interested in
  updating is not in there, you can upload it via OToL's curator tool
  (\textless{}https://tree.opentreeoflife.org/curator).
\item
  The alignment should be a gene alignment that was used to generate the
  tree. The original alignments are usually stored in a public
  repository such as TreeBase (Piel et al. 2009; Vos et al. 2012), DRYAD
  (\url{http://datadryad.org/}), or the journal were the tree was
  originally published. If the alignment is stored in TreeBase,
  \texttt{physcraper} can download it directly, either from the TreeBASE
  website (\url{https://treebase.org/}) or through the TreeBASE GitHub
  repository (SuperTreeBASE;
  \url{https://github.com/TreeBASE/supertreebase}). If the alignment is
  on another repository, or provided personally by the owner, a copy of
  it has to be downloaded by the user, and it's local path has to be
  provided as an argument.
\item
  A taxon name matching step is performed to verify that all taxon names
  on the tips of the tree are in the DNA character matrix and vice
  versa.
\item
  A ``.csv'' file with the summary of taxon name matching is produced
  for the user.
\item
  Unmatched taxon names are dropped from both the tree and alignment.
  Technically, just one matching name is needed to perform the searches.
  Please, see next section.
\item
  A ``.tre'' file and a ``.fas'' file containing only the matched taxa
  are generated and saved in the \texttt{inputs} folder to be used in
  the following steps.
\end{itemize}

@@

  Users can provide a search taxon that is either a more or a less
  inclusive clade relative to the ingroup of the original phylogeny. If
  the search taxon is more inclusive, the sequence search will be
  performed outside the MRCAT of the matched taxa, e.g., including all
  taxa within the family or the order that the ingroup belongs to. If
  the search taxon is a less inclusive clade, the users can focus on
  enriching a particular clade/region within the ingroup of the
  phylogeny.
\item
  The Basic Local Alignment Search Tool, BLAST {[}Altschul et al.
  (1990); altschul1997gapped{]} is used to identify similarity between
  DNA sequences within the search taxon in a nucleotide database, and
  the remaining sequences on the alignment. The BLAST command line tools
  (Camacho et al. 2009) are used for both web-based and local-database
  searches. 
\item
  A pairwise alignment-against-all BLAST search is performed. This means
  that each sequence in the alignment is BLASTed against DNA sequences
  in a nucleotide database constrained to the search taxon. Results from
  each one of these BLAST runs are recorded, and matched sequences are
  saved along with their corresponding identification numbers (accesion
  numbers in the case of the GenBank database). This information will be
  used later to store the whole sequences in a dedicated library within
  the physcraper folder, allowing for secondary analyses to run
  significantly faster.
\item
  The DNA sequence similarity search can be done on a local database
  that is easily setup by the user. In this case, the BLASTn algorithm
  is used to performs the similarity search.
\item
  The search can also be performed remotely, on the NCBI database. In
  this case, the bioPython BLAST algorithm is used to perform the
  similarity search.
\item
  Matched sequences below an e-value, percentage similarity, and outside
  a minimum and maximum length threshold are discarded. This filtering
  leaves out genomic sequences. All acepted sequences are asigned an
  internal identifier, and are further filtered.
\item
  Because the original alignments usually lack database id numbers, a
  filtering step is needed. Accepted sequences that belong to the same
  taxon of the query sequence, and that are either identical or shorter
  than the original sequence are discarded. Only longer sequences
  belonging to the same taxon as the orignal sequence will be considered
  further for analysis.
\item
  Among the remaining filtered sequences, there are usually several
  exemplars per taxon. Although it can be useful to keep some of them
  to, for example, investigate monophyly within species, there can be
  hundreds of exemplar sequences per taxon for some markers. To control
  the number of sequences per taxon in downstream analyses, 5 sequences
  per taxon are chosen at random. This number is set by default but can
  be modified by the user.
\item
  Reverse complement sequences are identified and translated.
\item
  Users can choose to perform a more ``cycles'' of sequence similarity
  search, by blasting the newly found sequences. This can be done
  iteratively, but by default only sequences in the alignment are
  blasted. \textbf{\emph{Is there an argument to control the number of
  cycles of blast searches with new sequences?}}
\item
  Accepted sequences are downloaded in full, and stored as a local
  database in a directory that is globally accesible
  (physcraper/taxonomy), so they are accesible for further runs.
\item
  A fasta file containing all filtered and processed sequences resulting
  from the BLAST search is generated for the user.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The software MUSCLE (Edgar 2004) is implemented to perform alignments.
\item
  First, all new sequences are aligned using default MUSCLE options.
\item
  Then, a MUSCLE profile alignment is performed, in which the original
  alignment is used as a template to align new sequences. This ensures
  that the final alignment follows the homology criteria established by
  the original alignment.
\item
  The final alignment is not further processed automatically. We
  encourage users to check it either by eye and perform manual
  refinement or using any of the many tools for alignment processing, to
  eliminate columns with no information.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  A gene tree is reconstructed for each alignment provided, using the
  software RAxML (Stamatakis 2014) with 100 classic bootstrap
  (Felsenstein 1985) replicates by default. The number of bootsrap
  replicates can be modified by the user. Other type of bootstrap that I
  think is not yet incorporated into physcraper is the Transfer
  Bootstrap Expectation (TBE) recently proposed in Lemoine et al.
  (2018).
\item
  The final result is an updated phylogenetic hypothesis for each of the
  genes provided in the alignment.
\item
  Tips on all trees generated by physcraper are defined by a taxon name
  space, allowing to perform comparisons and conflict analyses.
\item
  Robinson Foulds metrics
\item
  Describe what a conflict analysis is: Node by node comparison of the
  resulting clades compared to
\item
  For the conflict analysis to be meaningful, the root of the tree
  ineeds to be accurately defined.
\item
  Currently, the root is determined by finding the parent node of the
  sequences that do not belong to the ingroup/ search taxon. This
  ensures a correct rooting of the tree even when the search taxon is
  more inclusive than the ingroup.
\item
  Conflict information can only be generated in the context of the whole
  Open Tree of Life. Otherwise, it is not really possible to get
  conflict data. \textbf{\emph{- One way to compare two independent
  phylogenetic trees is to compare them both to the synthetic OToL and
  then measure how well they do against each other}}
\end{itemize}

@@

The genus \emph{Ilex} is the only extant clade within the family
Aquifoliaceae, order Aquifoliales of flowering plants. It encompasses
between 400-600 living species. A review of litterature shows that there
are three published phylogenetic trees, showing relationships within the
hollies. The first one has been made available both on OToL phylesystem
and synth tree, and on treeBASE, it samples 48 species. The second has
not been made available anywhere, not even in supplementary data of the
journal. \textbf{\emph{Contact authors? They seem old school, probably
do not wanna share their data.}} The most recent one has been made
available in the OToL Phylesystem and DRYAD. It is the best sampled yet,
with 200 species. However, it has not been added to the syntehtic tree
yet. This makes it a perfect case to test the basic functionalities of
physcraper: we know that the sequences of the most recently published
tree have been made available on the GenBank database (Benson et al.
2000; Wheeler et al. 2000). Updating the oldest tree, we should get
something very similar to the newest tree.

@@

Let's be more specific now about our X group and say it is the
Ascomycota. The best tree currently available in OToL was published by
Schoch et al. (2009). The first step, is to get the Open Tree of Life
study id. There are some options to do this: - You can go to the Open
Tree of Life website and browse until you find it, or - you can get the
study id using R tools: - By using the TreeBase ID of the study (which
is not fully exposed on the TreeBase website home page of the study, so
you have to really look it up manually):

@@

Phylogeny of the Testudines 6 tips from Crawford et al. (2012) There is
just one tree in OToL. There is just one alignment on
\href{https://treebase.org/treebase-web/search/study/matrices.html?id=12742}{treebase}
with all the 1 145 loci.

@@

Describe again statistics to compare phylogenies provided by physcraper
via OpenTreeOfLife. Mention statistics provided by other tools:
PhyloExplorer (Ranwez et al. 2009). Compare and discuss.

@@

How can it be used for the advantage of the field: - rapid phylogenetic
placing of newly discovered species, as mentioned in Webb et al. (2010)
- obtain trees for ecophylogenetic studies, as mentioned in Helmus and
Ives (2012) - one day could be used to sistematize nucleotide databases,
such as Genbank (Benson et al. 2000; Wheeler et al. 2000), as mentioned
in San Mauro and Agorreta (2010), i.e., curate ncbi taxonomic
assignations. - allows to generate custom species trees for downstream
analyses, as mentioned in Stoltzfus et al. (2013)

Things that physcraper does not do: - analyse the whole GenBank database
(Benson et al. 2000; Wheeler et al. 2000) to find homolog regions
suitable to reconstruct phylogenies, as mentioned in Antonelli et al.
(2017). There are already some very good tools that do that. - provide
basic statistics on data availability to assemble molecular datasets, as
mentioned by Ranwez et al. (2009). Phyloexplorer does this? - it is not
a tree repo, as phylota is, mentioned in Deepak et al. (2014)

@@

Sanderson et al. (2008)\strut

@@

finds sets of DNA homologs on the GenBank database; phylogenetic
reconstruction\strut

@@

Wu and Eisen (2008)\strut

@@

baited search; protein markers on phylogenomic data; personal database
of genomes or metagenomic data, manually downloaded either from a public
database or from private data; phylogenetic reconstruction\strut

@@

Smith et al. (2009)\strut

@@

Baited search of DNA markers on the GenBank database; phylogenetic
reconstruction\strut
